Superphy: Real-time prediction of \textit{E. coli} phenotype using graph-based genome sequence storage and retrieval with the \textit{spfy} module

### 2017-11-30 paper-webserver.tex
ADD: connecting sentances

% Need a sentance introducing the tools otherwise this sounds just like the intro section
Spfy performs reference laboratory tasks: O-antigen typing, H-antigen typing, and VF gene determination using , STX typing using Phylotyper \cite{whiteside2017phylotyper}, and AMR gene determination using the RGI program \cite{mcarthur2013comprehensive}. Spfy also performs bioinformatics analyses: pangenome generation using Panseq \cite{laing2010pan}, statistical significance testing of genome markers for user-defined groups, and AMR predictions using support vector machines (SVMs).

@@

\subsection{Real-time analysis pipelines}
% para
% 1. goals: real-time, support for pipelines (linked modules)
% 2. how pipelines have been handled in the past: Galaxy, other examples
% 3. Python, RQ
% para
% 1. how we implemented RQ
%	related: packaging of modules in conda

@@

Docker \url{https://www.docker.com/} is a virtualization technology to run self-contained operating systems on the same host computer.
lightweight...
The Spfy platform depends on a series of webservers, databases, and task workers and uses Docker to compartmentalize these services which are then networked together using Docker-Compose \url{https://docs.docker.com/compose/}.
(see Figure \ref{fig-docker})
Docker integration ensures that software dependencies, which are typically manually installed \cite{doi:10.1093/bioinformatics/btu153,laing2010pan,inouye2014srst2,naccache2014cloud}, are instead handled automatically. With compartmentalization of service runtimes, code failures can not propagate to other services.

>>>>

% Need a sentance introducing the tools otherwise this sounds just like the intro section
Prebuilt tools are available for a variety of reference laboratory tasks.
Spfy performs reference laboratory tasks: O-antigen typing, H-antigen typing, and VF gene determination using ECtyper \url{https://github.com/phac-nml/ecoli_serotyping}, STX typing using Phylotyper \cite{whiteside2017phylotyper}, and AMR gene determination using the RGI program \cite{mcarthur2013comprehensive}. Spfy also performs bioinformatics analyses: pangenome generation using Panseq \cite{laing2010pan}, statistical significance testing of genome markers for user-defined groups using SciPy \cite{jones2014scipy}, and support vector machine (SVM)-backed AMR predictions using Scikit-learn \cite{pedregosa2011scikit}.
These modules are used for the data-generation aspects of Spfy.

@@

\subsection{Service Virtualization}
% para
% 1. goals: real-time, support for pipelines (linked modules)
% 2. how pipelines have been handled in the past: Galaxy, other examples
% 3. Python, RQ
% para
% 1. how we implemented RQ
%	related: packaging of modules in conda

@@

% cost of docker < a full VM
% it's not quite a full OS
Docker \url{https://www.docker.com/} is a virtualization technology to simulate self-contained operating systems on the same host computer, without the overhead of full hardware virtualization \cite{felter2015updated}.
The Spfy platform depends on a series of webservers, databases, and task workers and uses Docker to compartmentalize these services which are then networked together using Docker-Compose \url{https://docs.docker.com/compose/}.
(see Figure \ref{fig-docker})
Docker integration ensures that software dependencies, which are typically manually installed \cite{doi:10.1093/bioinformatics/btu153,laing2010pan,inouye2014srst2,naccache2014cloud}, are instead handled automatically. With compartmentalization of service runtimes, code failures can not propagate to other services.
